---
title: "Modeling and prediction for movies"
output:
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
  pdf_document: default
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `movies`. Delete this note when before you submit 
your work. 

```{r load-data}
load("movies.Rdata")
```



* * *

## Part 1: Data
The rating is calculated based on customer reviews from a variety of platforms. Therefore, the average score given by a small number of samples (reviewer) is not exactly the same as the average score that would have been obtained if all users of the product posted a review. 
Also, consumers with extreme opinions are more likely to post reviews, which leads to being biased. Furthermore, Reviews also need to objectively measure performance. However, users who post reviews do not have the knowledge, equipment, and time to evaluate product performance in this way. Therefore, the measurement method of the review differs depending on the reviewer.
* * *

## Part 2: Research question
Is there a correlation between the IMDb rating and audience score?

I'm curious because the ratings have to equal if these reflect the parameter.


* * *

## Part 3: Exploratory data analysis
```{r Exploratory}
m1 <- lm(imdb_rating ~ audience_score, data = movies)
summary(m1)
```


```{r Exploratory1}
ggplot(data = movies, aes(x = audience_score, y = imdb_rating)) +
  geom_point()  +
  stat_smooth(method = "lm", se = FALSE)
```

The correlation coefficient is 2.2e-16
There is a positive correlation relationship.

* * *

## Part 4: Modeling

Full model
```{r Exploratory2}
M2 = lm(imdb_rating ~ audience_score + best_pic_nom + best_pic_win + best_actor_win + best_actress_win + best_dir_win, data = movies)
summary(M2)

```

```{r Exploratory3}
M3 = lm(imdb_rating ~ audience_score + best_pic_win + best_actor_win + best_actress_win + best_dir_win, data = movies)
summary(M3)

```

```{r Exploratory4}
M4 = lm(imdb_rating ~ audience_score + best_actor_win + best_actress_win + best_dir_win, data = movies)
summary(M4)

```
Using backwards elimination p-value, removed best_pic_nomyes and best_pic_win due to higher number of p-values.

### Model diagnostics
### 1, Linear relationship between audience_score and imdb_rating
### 2, Nearly normal residuals
```{r Exploratory5}
plot(M4$residuals ~ movies$audience_score)

```

### 3, Constant variability
```{r Exploratory6}
hist(M4$residuals)
qqnorm(M4$residuals)
qqline(M4$residuals)
```
```{r Exploratory7}
plot(M4$residuals ~ M4$fitted)
plot(abs(M4$residuals) ~ M4$fitted)
```
Except at the tail areas, we are not seeing huge deviations from the mean.

### 4, Independent
```{r Exploratory8}
plot(M4$residuals)
```

There is no pattern.
* * *

## Part 5: Prediction
$$IMDb Rating = 3.574+(0.046*63)+(0.12*0)+(0.137*0)+(0.2*0)=6.472$$
Actual IMDb Rating = 7

Reference(s)　https://www.rottentomatoes.com/m/passengers_2016
* * *

## Part 6: Conclusion
There is no huge difference between prediction and actual rating.
We can say the model I created was usefull for some extent.